Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-09 response/response.tex

    As far as I know, the company that developed Better Code Hub 
    developed also the Delta Maintainability Model [diBiase2019] 
    that aims at measuring the maintainability of a code change 
    and a score and compare change-based maintainability measurements.

    [diBiase2019] M. di Biase and A. Rastogi and M. Bruntink and A. van 
    Deursen. The Delta Maintainability Model: Measuring Maintainability 
    of Fine-Grained Code Changes. IEEE/ACM International Conference 
    on Technical Debt (TechDebt) in 2019.

\end{revcomment}

\Us Thank you for suggesting the Di Biase et al.'s paper. 
We evaluate the impact of security patches in software 
maintainability using an alternative maintainability model [Cruz2019].

Di Biase et al.'s work was developed in paralell with the one by Cruz et al [Cruz2019]. 
Both models attempt to measure maintainability, but Di Biase et al.'s is not as complete 
since it only considers $5$ of the same set of guidelines. Both models build a 
new maintainability model over the SIG-MM model---the model behind BCH.

@@

Our model was validated by DiBiase in several discussions between 
the authors of both papers.

We also mention Di Biase et al.'s work in our \textit{Related Work} section:
\begin{quote}
    Recent work
proposed a new maintainability model to 
measure fine-grained code changes by adapting/extending the BCH model [diBiase2019].
Our work uses the same base model (SIG-MM), but considers a broader set of guidelines. 
Moreover, we solely focus on evaluating the impact of security patches on software maintainability.
\end{quote}

@@

    Intro:
    \begin{itemize}
        \item First sentence - quality is not ONLY related to cost but also to security 
        and safety.
        \item Provide a URL to Software Improvement Group and Better Code Hub.
        \item Page 3, Line 1 - Application Security Verification Standard (ASVS).
        \item Page 3, Line 7 - instead of a "broad number of code metrics" - tell 
        us exactly the number of metrics.
        \item Page 3, Line 13 - "suggest" sounds more scientific than "hint at"
        \item Page 3, Line 24 - "we intend to highlight the need …". Is that the 
        broad goal of your paper?  The goal should be explicitly stated in the 
        abstract and intro.
    \end{itemize}
\end{revcomment}

\Us Thank you for reporting these issues. All of them were addressed in 
the new version of the paper. In the last point, where the reviewer asks ``Is that the 
broad goal of your paper?'', we want to clarify that the goal of our study
is to show the impact of security patches on software maintainability and
highlight the need for solutions which are described in the end of 
the abstract, Section 1 (\textit{Introduction}) and Section 5 (\textit{Study Implications}).

\begin{revcomment}[2.4]

    Intro:\\
    You should check out this paper: 
    [Li2017] Li, Frank and Paxson, Vern. A large-scale empirical study of security patches.
    ACM SIGSAC Conference on Computer and Communications Security in 2017.

@@

\end{revcomment}

\Us Thank you for bringing our attention to this paper. We now discuss
this paper in the Related Work section and used it to support some 
of our claims and findings.

We added the following paragraph to Section 7 (\emph{Related Work}):

\begin{quote}
    Researchers
performed a large-scale empirical study to understand the characteristics of security patches
and their differences against bug fixes [Li2017].
The main findings were that security patches are smaller and less complex compared
to bug fixes and usually performed at function-level. Our study compares
the impact of security patches on software maintainability with the impact 
of regular changes.
\end{quote}

We added the following information to Section 1 (\emph{Introduction}):

\begin{quote}
    Our hypothesis is that some of these patches may 
have a negative impact on the software maintainability and, 
possibly, even be the cause of the introduction of new 
vulnerabilities---harming software reliability and introducing 
technical debt. Research found that $34\%$ of the security patches 
performed introduce new problems and $52\%$ are incomplete and do not 
fully secure systems [Li2017].
\end{quote}

### 2021-02-09 paper/emse20.tex
section 5 fixes, 2.4 in progress

\textit{\textbf{Follow Best Practices:}} Developers are not 
paying attention to some quality aspects of their solutions/patches, 
as seen in Figure~\ref{fig:guidelines}, ending up harming 
software maintainability. We argue that developers
should design and implement solutions that respect the 
limit bounds of branch points and function/module sizes that are 
recommended by best practices to avoid increasing the 
size, complexity and dependencies of their patches.
Developers should also consider the threshold limit 
for parameters per function---to 
keep unit interfaces small and easy to use and understand.
Patterns such as \emph{Introduce Parameter Object} are useful 
to send information to a new function/class through an object
and keep the number of parameters small and the information well-organized.

@@

Researchers
performed a large-scale empirical study to understand the characteristics of security patches
and their differences against security bug fixes~\cite{10.1145/3133956.3134072}.
The main findings were that security patches are smaller and less complex compared
to bug fixes and usually performed at function-level.

Studying the evolution 
of maintainability issues during the development of Android apps, Malavolta et al. ($2018$)~\cite{8530041}
discovered that maintainability decreases over time. Palomba et al.
($2018$)~\cite{Palomba:2018:DIM:3231288.3231337} exhibits proof that code smells
should be carefully monitored by programmers since there is a high correlation
between maintainability aspects and proneness to changes/faults. In 2019, Cruz et 
al.~\cite{8919169} proposed a formula to calculate maintainability 
based on the BCH's guidelines and measured the impact of energy-oriented fixes 
on software maintainability. Recent work
proposed a new maintainability model to 
measure fine-grained code changes by adapting/extending the BCH model~\cite{8785997}.
The present work uses the same base model (SIG-MM), considers more guidelines and focuses 
solely on evaluating the impact of security patches on software maintainability.

>>>>

\textit{\textbf{Follow Best Practices:}} Developers are not 
paying attention to some quality aspects of their solutions/patches, 
as seen in Figure~\ref{fig:guidelines}, ending up harming 
software maintainability. We argue that developers
should design and implement solutions that respect the 
limit bounds of branch points and function/module sizes that are 
recommended by best practices to avoid increasing the 
size, complexity and dependencies of their patches.
Developers should also keep function parameters below 
the recommended limit. It helps keep unit interfaces small 
and easy to use and understand.
Patterns such as \emph{Introduce Parameter Object} are useful 
to send information to a new function/class through an object
and keep the number of parameters small and the information well-organized.

@@

Researchers
performed a large-scale empirical study to understand the characteristics of security patches
and their differences against bug fixes~\cite{10.1145/3133956.3134072}.
The main findings were that security patches are smaller and less complex compared
to bug fixes and usually performed at function-level. Our study compares
the impact of security patches on software maintainability with the impact 
of regular changes.

Studying the evolution 
of maintainability issues during the development of Android apps, Malavolta et al. ($2018$)~\cite{8530041}
discovered that maintainability decreases over time. Palomba et al.
($2018$)~\cite{Palomba:2018:DIM:3231288.3231337} exhibits proof that code smells
should be carefully monitored by programmers since there is a high correlation
between maintainability aspects and proneness to changes/faults. In 2019, Cruz et 
al.~\cite{8919169} proposed a formula to calculate maintainability 
based on the BCH's guidelines and measured the impact of energy-oriented fixes 
on software maintainability. Recent work
proposed a new maintainability model to 
measure fine-grained code changes by adapting/extending the BCH model~\cite{8785997}.
Our work uses the same base model (SIG-MM), but considers a broader set of guidelines. 
Moreover, we solely focus on evaluating the impact of security patches on software maintainability.
